D3692R1: How to Avoid OOTA Without Really Trying

### 2025-06-14 paper/ootavacuous.tex
ootavacuous: Section 7.4: Drop "simply", just "because"
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>
ootavacuous: Section 7.6: Expand "them" to "OOTA cycles"
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Although this result is unexpected, and while we don't recommend this sort of
code transformation, we cannot say that this conclusion is definitely
wrong, because one's intuitive notions of semantic dependency are not
always clear in cases involving multiple loads from the same variable.
% Can we instead say that transforming the code might require that the
% witness also be transformed?
In the unlikely event that this transformation proves useful, there
will be a community process that determines whether the value of this
transformation is worth the added conceptual load on developers.
Until that time, pure mathematics cannot help us simply because it is
impossible to say whether or not there is a semantic dependency from
\co{y} to \co{z} without reference to a specific implementation.

@@

As noted in Section~\ref{sec:Brief OOTA Overview}, the C++
standard explicitly recommends against them in 33.5.4p8
(\co{[atomics.order]})~\cite{ThomasKoeppe2023N4950}:
\begin{quote}
	Implementations should ensure that no ``out-of-thin-air'' values
	are computed that circularly depend on their own computation.
\end{quote}

>>>>

Although this result is unexpected, and while we don't recommend this sort of
code transformation, we cannot say that this conclusion is definitely
wrong, because one's intuitive notions of semantic dependency are not
always clear in cases involving multiple loads from the same variable.
% Can we instead say that transforming the code might require that the
% witness also be transformed?
In the unlikely event that this transformation proves useful, there
will be a community process that determines whether the value of this
transformation is worth the added conceptual load on developers.
Until that time, pure mathematics cannot help us because it is
impossible to say whether or not there is a semantic dependency from
\co{y} to \co{z} without reference to a specific implementation.

@@

As noted in Section~\ref{sec:Brief OOTA Overview}, the C++
standard recommends against OOTA cycles in 33.5.4p8
(\co{[atomics.order]})~\cite{ThomasKoeppe2023N4950}:
\begin{quote}
	Implementations should ensure that no ``out-of-thin-air'' values
	are computed that circularly depend on their own computation.
\end{quote}
